Modelling BCG vaccination in the UK

### 2019-06-17 rmds/04-tb-epi-england.Rmd
reorganised thesis to work with online gitbook
Former-commit-id: 3fd8c59438bc22ef6b09d75159886a79ea855f4e
pushing fixes
edit TB epi chapterr

Whilst the characteristics of tuberculosis in England have been reported elsewhere,@PHE2017 and key risk factors such as non-UK birth status have been identified,@French2007 little attention has been given to the role of BCG vaccination. In particular, there is little information available regarding the demographics of vaccinated versus unvaccinated cases and the impact of BCG vaccination on TB outcomes in England has not been explored. There has also only been limited reporting of the age distribution, and trends over time, in incidence rates stratified by UK birth status.

@@

```{r load-ets, messages = FALSE}
if (regen_results) {
  ets <- readRDS("../data/tbinenglanddataclean/clean_ets_2016.rds")
}
```

>>>>

Whilst the characteristics of tuberculosis in England have been reported elsewhere,[@PHE2017; @PHE2018] and key risk factors such as non-UK birth status have been identified,@French2007 little attention has been given to the role of BCG vaccination. In particular, there is little information available regarding the demographics of vaccinated versus unvaccinated cases and the impact of BCG vaccination on TB outcomes in England has not been explored. There has also only been limited reporting of the age distribution, and trends over time, in incidence rates stratified by UK birth status.

@@

```{r load-ets, messages = FALSE}
if (regen_results) {
  ets <- readRDS("../data/tbinenglanddataclean/clean_ets_2016.rds")

}
```
